The 2- and 3-point surface correlation functions calculations: from novel exact continuous approach to improving methodology for discrete images

### 2023-05-17 paper.tex
Start a new paragraph

In this contribution we continue to build upon foundational work of Ma and
Torquato \cite{ma2018SS} and recent findings of Samarin et al. \cite{Samarin} to
develop a robust and efficient approach to compute surface correlation functions
from digital 2D and 3D images. In particular, here our aim is to establish a
direct verification of "discrete" methodology (that is easily parallelizable on
CPU and GPU architectures) using exact "continuous" approach for arbitrary
structures (still described by some continuous function). The rest of the
manuscript is organized as follows: in \cref{sec:def} we introduce some major
definitions of CFs necessary for establishing algorithms, in \cref{sec:algo} we
describe the all methodological details for "discrete" method for digital
images. Next, in \cref{sec:algo-precise} we explain in detail why verification
of computational approaches for digital images is currently hampered, and then
introduce novel exact "continuous" methodology in \cref{sec:fss-2d}. The choice
of verification cases is presented in \cref{sec:results} followed by
improvements in methodology of Samarin et~al. The paper concludes with
discussion, outline and summary in \cref{sec:summary}.

>>>>

In this contribution we continue to build upon foundational work of Ma and
Torquato \cite{ma2018SS} and recent findings of Samarin et al. \cite{Samarin} to
develop a robust and efficient approach to compute surface correlation functions
from digital 2D and 3D images. In particular, here our aim is to establish a
direct verification of "discrete" methodology (that is easily parallelizable on
CPU and GPU architectures) using exact "continuous" approach for arbitrary
structures (still described by some continuous function).

The rest of the manuscript is organized as follows: in \cref{sec:def} we
introduce some major definitions of CFs necessary for establishing algorithms,
in \cref{sec:algo} we describe the all methodological details for "discrete"
method for digital images. Next, in \cref{sec:algo-precise} we explain in detail
why verification of computational approaches for digital images is currently
hampered, and then introduce novel exact "continuous" methodology in
\cref{sec:fss-2d}. The choice of verification cases is presented in
\cref{sec:results} followed by improvements in methodology of Samarin et~al. The
paper concludes with discussion, outline and summary in \cref{sec:summary}.
